---
title: "Mlflow Introduction" 
execute:
  echo: true # show code
format: 
  html: # output format
    embed-resources: true # create a self-contained html
    code-fold: true # if we show code, use as fold
    theme: 
      - cosmo # a html theme (try sketchy or darkly)
      - custom.scss # additional custom scss
    toc: true # table of content
    number-depth: 3 # deepest level 
    toc-title: Contents # content title
    toc-location: left # toc alignment
    number-sections: true # use numbering
    html-math-method: mathjax # displays mathematical notation 
    smooth-scroll: true # smooth scrolling
---

The MLflow R API allows you to use MLflow Tracking, Projects and Models.

To use the MLflow R API, you must first set up MLflow in Python (see the [mlflow-setup tutorial](../mlflow-setup.md)). 

Start R inside VS Code or RStudio and install the MLflow Python package:

```{r}
install.packages('mlflow')
```


Activate mlflow:

```{r}
library(mlflow)
library(sys)
```


```{r}
mlflow_ui()
```


Next, we need to set the MLFLOW_PYTHON_BIN and MLFLOW_BIN environment variables to specify the Python and MLflow binaries to use. By default, the R client automatically finds them using Sys.which('python') and Sys.which('mlflow').

```{r}
Sys.setenv(MLFLOW_PYTHON_BIN='/Users/jankirenz/miniconda3/envs/mlflow/bin/python')
```


```{r}
Sys.setenv(MLFLOW_BIN='/Users/jankirenz/miniconda3/envs/mlflow/bin/mlflow')
```


The MLflow *Tracking API* lets you log metrics and artifacts (files) from your data science code and see a history of your runs. You can try it out by writing a simple R script as follows (this example is also included in quickstart/mlflow_tracking.py):

```{r}

```



```{r}
library(mlflow)


# Log a parameter (key-value pair)
mlflow_log_param("param1", 5)

# Log a metric; metrics can be updated throughout the run
mlflow_log_metric("foo", 1)
mlflow_log_metric("foo", 2)
mlflow_log_metric("foo", 3)

# Log an artifact (output file)
writeLines("Hello world!", "output.txt")
mlflow_log_artifact("output.txt")

```
